Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-17 Article.tex
Correction of Introduction chapter

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[colorlinks = true]{hyperref}

@@

@@

\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation--extrapolation capacity validation}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
\address[ETS]{Écolde de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}

@@

\begin{keyword}
Zerilli--Armstrong flow law \sep Constitutive behavior \sep Arhenius--flow law \sep Hansel--Spittel flow law \sep Johnson--Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
\end{keyword}

@@

%--------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%--------------------------------------------------------------------------
Continuous casting and rolling mechanisms are an integral part of the technological methods of medium deformation through a continuous water-cooled crystalliser before entering a rolling mill. Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation . Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{He-2013}. However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions . Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{Changizian-2012}. To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials . FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism. For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{Qin-2010, Mandal-2009, Ji-2018}.

Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{Ashtiani-2012}. Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials. The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions. To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{Lin-2008-P,Wu-2012}.

Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models. Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{Lin-2011,Shin-2010,Rusinek-2010}. As for the semi-empirical models, they try to be at the border between the empirical and physical models. Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983, Johnson-1985} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987} models are the best known and available in finite element codes. The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004, NematNasser-2003}. However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material. We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021}. To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}. According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}. However, the drawbacks of this model are related to the temperature limit value of the test. Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}. In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{Jonas-1969,Zhang-2012,Mostafaei-2012}. Its original formulation has been revised several times in order to properly describe the obtained experimental behavior. In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several researchers. For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy. Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.

The method based on artiﬁcial neural networks is an approach to predict the deformation behavior of materials under different conditions. ANN is in fact a method originally developed to simulate the biological processes of the human brain. And therefore it is not necessary to formulate a mathematical expresson and identify these parameters for this kind of model. The response of the deformation behavior of materials is highly non-linear at high temperatures, and many factors affecting the deformation behavior of materials are also non-linear; this makes the accuracy of the flow stress predicted by regression methods and the appropriate range is limited. Faced with these limitations, ANN models are therefore of interest.  Indeed, ANNs are particularly suited to deal with complex and non-linear relationships; consequently, ANNs have been successfully applied to predict the deformation behavior of materials under hot working conditions. ANNs can provide a fundamentally different approach to statistical or numerical techniques for materials modelling and materials processing control.

In this study, the high temperature deformation behavior of AISI P20 modified carbon steel subjected to compression tests will be highlighted. From the experimental data obtained, analytical models will be identified on the one hand in order to select the one that could better describe the behavior of this alloy and on the other hand, an ANN model is also developed and a comparative study between the analytical models and the ANN model will follow. A fundamental issue that will also be addressed in this work is the ability to interpolate and extrapolate of the developed models. Indeed, how do models behave when it comes to interpolating or extrapolating data that the model is never aware of ? the answer to this question will be well analyzed in this study.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the material et experimental procedure inverstigated in this study. Section \ref{sec:ConstLaws} is devoted to the presentation of the models developed and their comparative. Section \ref{sec:inExtrapolation} details the validation of interpolation and extrapolation capacity of each model developped. Conclusion and future works are detailed in Section \ref{sec:Conclusion}.

@@

The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature . However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows \cite{Johnson-1985}:

@@

The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates. All parameters of JC model are in Table \ref{tab: JCparameters}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model}
\label{fig:iCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
\hline
\label{tab: JCparameters}
\end{tabular}
\end{table}
%-------------------------------------------------------------------------
\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011}. But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener--Hollomon parameter is introduced whose expression is given as follows:

>>>>

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
%\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[colorlinks = true]{hyperref}

@@

% This is used to add comments into the text
\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}\\#1}}\endgroup} }

@@

\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation-extrapolation capacity validation}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}

@@

\begin{keyword}
Zerilli-Armstrong flow law \sep Constitutive behavior \sep Arhenius flow law \sep Hansel-Spittel flow law \sep Johnson-Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
\end{keyword}

@@

%--------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%--------------------------------------------------------------------------
Continuous casting and rolling techniques are an integral part of material forming methods. Advantages of this method include increased process efficiency, energy savings, improved casting quality and easier mechanization and automation. Deformation, a complex process involving simultaneous elastic and plastic deformation, is accompanied by high temperatures, high strain rates, and complex and variable frictional conditions \cite{He-2013}, for which, analytical methods are not available for quantitative study and analysis of the deformation mechanism. On the other hand, conducting experimental tests is not only time-consuming but also requires a high financial investment \cite{Changizian-2012}. As an alternative approach to the previous two, the Finite Element Method (FEM) is widely used as a tool for analysis and optimization of process parameters in the processing of various materials. Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms. For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Qin-2010, Mandal-2009, Ji-2018}.

Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties \cite{Ashtiani-2012}. Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and re-crystallization), which very often occur during hot working, influence the behavior and deformation of materials. The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions. To this end, a mathematical formulation is typically used to represent the flow of a material in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.

For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models. Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}. Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983, Johnson-1985} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes. The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}. However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior. We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}. To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}. Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}. However, this model has other drawbacks related to the limit value of the test temperature. Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}. In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.

The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Zhang-2012, Mostafaei-2012}. Its original formulation has been revised several times to correctly describe the resulting experimental behavior. In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors. For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that his model could predict the high-temperature flow of a magnesium alloy. Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.

\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}

Behavior modeling based on an artificial neural network is an approach to predict the flow of materials without requiring a mathematical formulation of the flow law. It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model. Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress by an analytical model whose parameters are identified by a classical regression method is limited. Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships. Consequently, ANNs have been successfully applied to predict the flow of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}. They provide a fundamentally different approach to statistical or numerical techniques for modeling materials.

In this work, the high-temperature thermomechanical behavior of AISI P20 modified carbon steel subjected to compression tests in a Gleeble thermomechanical simulator was studied. From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy. A flow model based on an artificial neural network was also developed and identified, and a comparative study between the five analytical models and the ANN model is proposed. A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study. Section \ref{sec:ConstLaws} is devoted to the presentation of the five analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models. Section \ref{sec:inExtrapolation} details the interpolation and extrapolation capabilities of each model proposed in this paper. Conclusions and future work are detailed in Section \ref{sec:Conclusion}.

@@

The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature. However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows \cite{Johnson-1985}:

@@

The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates. All parameters of JC model are in Table \ref{tab: JCparameters}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model}
\label{fig:iCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
\hline
\label{tab: JCparameters}
\end{tabular}
\end{table}
%-------------------------------------------------------------------------
\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}. But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:
